Homicide Increases in the COVID-19 Era

### 2025-03-07 Draft3.qmd
Got rid of warnings and messages in embedded code blocks w warning and message FALSE

@@

```{r, echo=FALSE}
crime_la$DateParsed <- as.POSIXct(crime_la$Date.Rptd, 
                                  format = "%m/%d/%Y %I:%M:%S %p", 
                                  tz = "America/Los_Angeles")

@@

```{r, echo=FALSE, fig.cap = "Crime Occurrences by Day of the Week", message=FALSE}
# Convert Date.Rptd to Date format (ignore time part)
#crime_la$Date.Rptd
crime_la$Date <- as.Date(substr(crime_la$Date.Rptd, 1, 10), format = "%m/%d/%Y")

@@

```{r, echo=FALSE}
# Remove missing values and empty strings in Vict.Sex column
crime_la <- subset(crime_la, Vict.Sex != "" & !is.na(Vict.Sex))

@@

```{r, echo=FALSE}
zcta <- read_sf(dsn = "0_Data/Raw_Data/cb_2020_us_zcta520_500k", layer = "cb_2020_us_zcta520_500k")
LA_zctas <- read.csv("0_Data/Raw_Data/zctas.csv") #obtained using zipcodeR::search_city("Los Angeles", "CA") and then checking which zip codes are also ZCTAs

@@

```{r, echo=FALSE}
# quantiles for the entire dataset (from 2018 to 2023) to divide the median income into groups
qntls <- round(quantile(zcta_no_NAs$S1903_C03_001E, probs = seq(0, 1, length.out = 7)), 0)

@@

```{r, echo=FALSE}
# using latitude and longitude to obtain the zip codes of the crime locations
# crime_la$year <- as.integer(stringr::str_sub(crime_la$YearWeek, 1, 4))
# id_lat_long_crime_la <- subset(crime_la, select = c("LAT", "LON", "DR_NO", "year"))

@@

```{r, echo=FALSE}
# fix mistake
evictions_la$Date.Received <- gsub("2205", "2025", evictions_la$Date.Received)

@@

```{r, echo=FALSE}
crime_la$year <- lubridate::year(crime_la$DateParsed)
crime_by_area <- crime_la %>% group_by(AREA.NAME, year) %>% summarize(numberOfCrimes = n()) %>% ungroup()

@@

```{r, echo=FALSE}
library(lubridate)
# creating dataset for correlations

@@

```{r, echo=FALSE}
homicide_by_gender <- crime_la %>% filter(Crm.Cd.Desc == "CRIMINAL HOMICIDE") %>% select(Vict.Sex, DateParsed, Vict.Age) %>% mutate(gender = factor(Vict.Sex))

@@

```{r, echo=FALSE}
crime_la$time <- sprintf("%04d",crime_la$TIME.OCC)
crime_la$Hour <- as.numeric(substr(as.character(crime_la$time), start = 1, stop = 2))

@@

```{r, echo=FALSE}
# Data Preparation
homicides <- crime_la %>% inner_join(crimes_with_zips, by = c("DR_NO", "LAT", "LON","X", "year")) %>% filter(Crm.Cd.Desc == "CRIMINAL HOMICIDE") %>% 
  mutate(date = as.Date(DateParsed),
         zip = as.character(ZCTA5CE20)) %>% select(-X)

@@

@@

```{r, echo=FALSE}
library(broom)

@@

```{r, echo=FALSE}
lm_income_crimes <- lm(number_of_crimes ~ cali_median_income, data = crime_income_per_zip)

@@

```{r, echo=FALSE, warning=FALSE}
homicides_latlon_rounded <- homicides %>% mutate(LAT_rounded = round(LAT, 1),
                                                 LON_rounded = round(LON, 1))
homicides_lat_long <- homicides_latlon_rounded %>% group_by(LAT_rounded, LON_rounded) %>% summarize(HomicideCount = n()) %>% ungroup()

@@

### By Year
```{r}
homicides_lat_long <- homicides_latlon_rounded %>% group_by(LAT_rounded, LON_rounded) %>% summarize(HomicideCount = n()) %>% ungroup()

>>>>

[ADD MAIN EDA TAKEAWAYS HERE]

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
crime_la$DateParsed <- as.POSIXct(crime_la$Date.Rptd, 
                                  format = "%m/%d/%Y %I:%M:%S %p", 
                                  tz = "America/Los_Angeles")

@@

```{r, echo=FALSE, fig.cap = "Crime Occurrences by Day of the Week", warning=FALSE, message=FALSE}
# Convert Date.Rptd to Date format (ignore time part)
#crime_la$Date.Rptd
crime_la$Date <- as.Date(substr(crime_la$Date.Rptd, 1, 10), format = "%m/%d/%Y")

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Remove missing values and empty strings in Vict.Sex column
crime_la <- subset(crime_la, Vict.Sex != "" & !is.na(Vict.Sex))

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
zcta <- read_sf(dsn = "0_Data/Raw_Data/cb_2020_us_zcta520_500k", layer = "cb_2020_us_zcta520_500k")
LA_zctas <- read.csv("0_Data/Raw_Data/zctas.csv") #obtained using zipcodeR::search_city("Los Angeles", "CA") and then checking which zip codes are also ZCTAs

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# quantiles for the entire dataset (from 2018 to 2023) to divide the median income into groups
qntls <- round(quantile(zcta_no_NAs$S1903_C03_001E, probs = seq(0, 1, length.out = 7)), 0)

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# using latitude and longitude to obtain the zip codes of the crime locations
# crime_la$year <- as.integer(stringr::str_sub(crime_la$YearWeek, 1, 4))
# id_lat_long_crime_la <- subset(crime_la, select = c("LAT", "LON", "DR_NO", "year"))

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# fix mistake
evictions_la$Date.Received <- gsub("2205", "2025", evictions_la$Date.Received)

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
crime_la$year <- lubridate::year(crime_la$DateParsed)
crime_by_area <- crime_la %>% group_by(AREA.NAME, year) %>% summarize(numberOfCrimes = n()) %>% ungroup()

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(lubridate)
# creating dataset for correlations

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
homicide_by_gender <- crime_la %>% filter(Crm.Cd.Desc == "CRIMINAL HOMICIDE") %>% select(Vict.Sex, DateParsed, Vict.Age) %>% mutate(gender = factor(Vict.Sex))

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
crime_la$time <- sprintf("%04d",crime_la$TIME.OCC)
crime_la$Hour <- as.numeric(substr(as.character(crime_la$time), start = 1, stop = 2))

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Data Preparation
homicides <- crime_la %>% inner_join(crimes_with_zips, by = c("DR_NO", "LAT", "LON","X", "year")) %>% filter(Crm.Cd.Desc == "CRIMINAL HOMICIDE") %>% 
  mutate(date = as.Date(DateParsed),
         zip = as.character(ZCTA5CE20)) %>% select(-X)

@@

[BASED ON THESE PLOTS, WE WILL DO XYZ TO EXAMINE ABC]

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(broom)

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
lm_income_crimes <- lm(number_of_crimes ~ cali_median_income, data = crime_income_per_zip)

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
homicides_latlon_rounded <- homicides %>% mutate(LAT_rounded = round(LAT, 1),
                                                 LON_rounded = round(LON, 1))
homicides_lat_long <- homicides_latlon_rounded %>% group_by(LAT_rounded, LON_rounded) %>% summarize(HomicideCount = n()) %>% ungroup()

@@

### By Year
```{r, echo=FALSE, warning=FALSE, message=FALSE}
homicides_lat_long <- homicides_latlon_rounded %>% group_by(LAT_rounded, LON_rounded) %>% summarize(HomicideCount = n()) %>% ungroup()
